The 4th Workshop on Sustainable Software: Best Practices and Experiences (WSSSPE4)

### 2016-06-10 WSSSPE4_proposal/WSSSPE4_proposal.tex
Added my funding
and fixed a typo

The National Center for Supercomputing Applications (NCSA) at the University of Illinois (U of I) will be the lead fiscal institution for this proposal to the Office of Advanced Cyberinfrastructure (ACI) at the National Science Foundation. NCSA staff will manage the travel for the participants and presenters funded through this proposal. US participants and presenters will arrange their flights through the travel agency of NCSA/University of Illinois, with reimbursed by NCSA/University of Illinois. The WSSSPE~2 organizing committee will review the applications and select the participants to be funded through this award.

@@

{\bf Gabrielle D. Allen}
\textcolor{red}{todo...}

>>>>

The National Center for Supercomputing Applications (NCSA) at the University of Illinois (U of I) will be the lead fiscal institution for this proposal to the Office of Advanced Cyberinfrastructure (ACI) at the National Science Foundation. NCSA staff will manage the travel for the participants and presenters funded through this proposal. U.S. participants and presenters will arrange their flights through the travel agency of NCSA/University of Illinois, with reimbursed by NCSA/University of Illinois. The WSSSPE4 organizing committee will review the applications and select the participants to be funded through this award.

@@

{\bf Gabrielle D. Allen}
was the PI for two recent workshop awards related to sustainable software. NSF CCF-1551592, made to the University of Illinois for \$88,739 for the period 09/15/2015 to 5/31/2017 supported the workshop on Computational Science \& Engineering Software Sustainability and Productivity Challenges (CSSSPE) which was hosted by NITRD and supported by NSF, DOE and DOD and brought together a very diverse number of agency representatives, software developers and software engineers spanning academia, national labs and industry. A report from this workshop is imminent. 
Allen was also PI for a previous awards supporting WSSSPE2 and 3, NSF ACI-1434218, made to the University of Illinois for \$24,758 for the period 5/1/2014 to 4/30/2016. The award funded participation at WSSSPE2 and WSSSPE3 by early career researchers and underrepresented groups.
